---
title: "RUL Model Evaluation"
format: html
editor: visual
---

```{r}
rm(list=ls())
library(tidyverse)
```

### Import Data

```{r}
# Import Data
df_fd001 <- read_delim('~/Documents/turbofan_predicitve_maintenance/CMaps/train_FD003.txt', delim = ' ', col_names = FALSE)

```

### Add names for variables

```{r}
# Variable known names
vari <- c('unit', 'time', 'ops1', 'ops2', 'ops3')

# Add names for sensors
for (i in 1:25){
   vari <- append(vari, paste('sen', i, sep = ''))
}

# Change variable names
colnames(df_fd001) <- vari
  
```

### EDA

There should be 100 engines in the train_FD001 data set.

```{r}
n_distinct(df_fd001$unit)
```

#### Summary Statistics

#### Units, Time and Operation Settings (ops)

```{r}
df_fd001 %>%
  select(unit, time, ops1, ops2, ops3) %>%
  summary()
```

We can see from the chart above, the average `time` or cycles, is a little over 139 cycles. The distribution of `ops1` is evenly distributed around the mean, where as `ops2` is skewed to the right. `ops3` on the other hand is uniformly distributed across all engines.

**Sensors**

```{r}
df_fd001 %>%
  select(sen1:sen23) %>%
  summary()
```
